Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Deep learning-based CSI feedback for RIS-assisted multi-user systems

@@

>>>>

\cite{guo2023ris}Proposes RIS-CoCsiNet, a cooperative CSI feedback framework for RIS-assisted systems that separates RIS-UE CSI into shared (among nearby UEs) and unique components. Achieves 8.93 dB NMSE improvement over conventional phase feedback at 0.5 BPD through magnitude-dependent phase feedback (MDPF) strategies. The distributed architecture reduces redundant feedback by 17-50\% for UEs within 0.3m spacing without requiring UE modifications.

@@

	\bibitem{guo2023ris}
	 J. Guo, X. Yang, C.-K. Wen, S. Jin, and G. Y. Li, ``Deep learning-based CSI feedback for RIS-assisted multi-user systems,'' \textit{arXiv preprint arXiv:2003.03303}, 2023.
